Robotic Cart System

### 2021-09-14 paperIEEE-ROSE2021-BrBeAlShMi.tex
Gramatical changes based on feedback

Abundant research carried out in the field of mobile robotics shows various ways to develop
robotic carts that will help consumers in carrying groceries through stores.
See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. The operating principle of several robotic carts available in the market focuses on a few different methods of having a
robotic cart interface with the customer and follow them through the store. One such method that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmission technology is shown in Fig.~\ref{fig:CompaRob}~\cite{Sales2016-CompaRob}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob robot~\cite{Sales2016-CompaRob}.}
   \label{fig:CompaRob}
 \end{figure}
% 
 Authors in~\cite{islam_lam_fukuda_kobayashi_kuno_2019} have developed a shopping
 support robot that employs a GRU (Gated Recurrent Unit) network to detect
 shopping habits of customers. The robot is also equipped with a LiDAR (Light
 Detection and Ranging) sensor and camera for detecting and building map of the
 customer's position using a two-dimensional skeleton and follow the customer
 through the store. The robot developed using such an algorithm is  shown in Fig.~\ref{fig:ShoppingSup}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.35\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping support robot.}
   \label{fig:ShoppingSup}
\end{figure}
%
Fig.~\ref{fig:SmartCart} shows a smart cart robot that has been developed by the authors in~\cite{Rawashdeh2017-Person}. The authors utilized an Arduino MEGA 2560, six
ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android
Studio IDE device, and Bluetooth for detecting a customer and following them
through the store. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.40\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}
%
The operating principle of the proposed prototype of a smart robotic cart relies mainly on the radio frequency identification technology. For that, RF modules, XBee S2C RF radios, are primarily utilized to identify and communicate between the robotic cart and the remote (customer in a store, for example). XBee S2C RF radios are inexpensive and easily configurable. An RF module is configured as a remote target device that is carried
by the user/customer. The robot will be able to track this remote instead of using line
of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
radios, the robot is equipped with a parabolic reflector, which improves radio
reception at various distances and angles,~\textit{i.e.,} angle of arrivals of
RF signals from the remote, based on research done previously in this type of
robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}. The approach using signal strengths of RF signals also requires an understanding
of multipath interference which is common in RF based wireless positioning
sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
course estimation calculations such as the received signal strength indicator (RSSI)
 together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath
interference.

@@

As can be seen, two subsystems (mobile cart and remote) of the proposed robotic cart communicate with one another by relaying radio messages between them. Fig.~\ref{fig:remote_block_diag} shows the block diagram of the remote. %
%
\begin{figure}[htbp]
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{}
    \label{fig:remote_block_diag}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{}
    \label{fig:mobile_block_diag}
  \end{subfigure}
  \caption{Block diagrams showing inputs and outputs of:~\subref{fig:remote_block_diag} remote and~\subref{fig:mobile_block_diag}~mobile cart of the proposed smart robotic cart.}
  \label{fig:blockDiagramRemoteMobileCart}
\end{figure}
%
It requires an RF module, XBee, attached to $7.4~[\si{\volt}]$ Li-Po battery
with a voltage regulation circuit since the XBee has a smaller input voltage of
$3.3~[\si{\volt}].$ The two inputs of the remote are the battery power and the
incoming RF messages which are passed through the RF transceiver. The remote
outputs the RF message back to the mobile cart, which will be discussed
later. The subsystem block diagram of the mobile cart is shown in
Fig.~\ref{fig:mobile_block_diag}. The cart requires a power source, which will
be a $7.4~[\si{\volt}],$ $8000~[\si{\milli\ampere\hour}]$ Li-Po battery since the Li-Po works well with powering the
embedded computer. The power to the subsystem will be toggled
by an on/off switch located on the chassis of the robotic cart. The final input
to the mobile cart subsystem are the incoming RF signals and the wheel velocities for the cart's actuators. These incoming RF
signals are passed to the direction sensitive RF receivers which output the
signals to the dual-direction multiplexer. The dual-direction multiplexer then
takes the four inputs from the direction sensitive RF receivers and passes one
output into the embedded computer. Once the embedded computer gets these signals
it can apply localization and navigation algorithms and pass the necessary actuator commands to the actuators of the robotic cart.

>>>>

Abundant research carried out in the field of mobile robotics shows various ways to develop
robotic carts that will help consumers in carrying groceries through stores.
See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. The operating principle of several robotic carts available in the market focuses on a few different methods of having a
robotic cart interface with the customer and follow them through the store. One such method that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmission technology is shown in Fig.~\ref{fig:CompaRob}~\cite{Sales2016-CompaRob}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob robot~\cite{Sales2016-CompaRob}.}
   \label{fig:CompaRob}
 \end{figure}
% 
 Authors in~\cite{islam_lam_fukuda_kobayashi_kuno_2019} have developed a shopping
 support robot that employs a GRU (Gated Recurrent Unit) network to detect
 shopping habits of customers. The robot is also equipped with a LiDAR (Light
 Detection and Ranging) sensor and camera for detecting and building map of the
 customer's position using a two-dimensional skeleton and follow the customer
 through the store. The robot developed using such an algorithm is  shown in Fig.~\ref{fig:ShoppingSup}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.35\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping support robot.}
   \label{fig:ShoppingSup}
\end{figure}
%
Fig.~\ref{fig:SmartCart} shows a smart cart robot that has been developed by the authors in~\cite{Rawashdeh2017-Person}. The authors utilized an Arduino MEGA 2560, six
ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android
Studio IDE device, and Bluetooth for detecting a customer and following them
through the store. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.40\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}
%
The operating principle of the proposed prototype of a smart robotic cart relies mainly on the radio frequency identification technology. For that, RF modules, XBee S2C RF radios, are primarily utilized to identify and communicate between the robotic cart and the remote (customer in a store, for example). XBee S2C RF radios are inexpensive and easily configurable. An RF module is configured as a remote target device that is carried
by the user/customer. The robot will be able to track this remote instead of using line
of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
radios, the robot is equipped with a parabolic reflector. This reflector helps improves radio reception at various distances and angles,~\textit{i.e.,} the angle of arrival of
the RF signals from the remote. This reflector setup is based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}. The approach using signal strengths of RF signals also requires an understanding
of multipath interference which is common in RF based wireless positioning
sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
course estimation calculations such as the received signal strength indicator (RSSI) together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath interference.

@@

As can be seen, two subsystems (mobile cart and remote) of the proposed robotic cart communicate with one another by relaying radio messages between them. Fig.~\ref{fig:remote_block_diag} shows the block diagram of the remote. %
%
\begin{figure}[htbp]
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{}
    \label{fig:remote_block_diag}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{}
    \label{fig:mobile_block_diag}
  \end{subfigure}
  \caption{Block diagrams showing inputs and outputs of:~\subref{fig:remote_block_diag} remote and~\subref{fig:mobile_block_diag}~mobile cart of the proposed smart robotic cart.}
  \label{fig:blockDiagramRemoteMobileCart}
\end{figure}
%
It requires an RF module, XBee, attached to $7.4~[\si{\volt}]$ Li-Po battery
with a voltage regulation circuit since the XBee has a smaller input voltage of
$3.3~[\si{\volt}].$ The two inputs of the remote are the battery power and the
incoming RF messages which are passed through the RF transceiver. The remote
outputs an RF message back to the mobile cart, which will be discussed
later. The subsystem block diagram of the mobile cart is shown in
Fig.~\ref{fig:mobile_block_diag}. The cart requires a power source, which will
be a $7.4~[\si{\volt}],$ $8000~[\si{\milli\ampere\hour}]$ Li-Po battery since the Li-Po works well with powering the
embedded computer. The power to the subsystem will be toggled
by an on/off switch located on the chassis of the robotic cart. The final input
to the mobile cart subsystem are the incoming RF signals and the wheel velocities for the cart's actuators. These incoming RF
signals are passed to the direction sensitive RF receivers which output the
signals to the dual-direction multiplexer. The dual-direction multiplexer then
takes the four inputs from the direction sensitive RF receivers and passes one
output into the embedded computer. Once the embedded computer gets these signals
it can apply localization and navigation algorithms and pass the necessary actuator commands to the actuators of the robotic cart.
